26 Years of Water Quality Change in Rhode Island Lakes and Ponds

### 2019-02-01 manuscript/manuscript.Rmd
first line of results text for state trends!

(`r fig_num(name = "temp_ri", caption = "Yearly trend over 20+ years of lake temperature in Rhode Island lakes and ponds.", display = "cite")`).

>>>>

Across the years of this study, average yearly scaled temperature in lakes and ponds appear to be increasing (Kendall's Tau: `r` , p-value: `r`) with the large majority of years with average temperature greater than the long term average occuring in the years since 2000 (`r fig_num(name = "temp_ri", caption = "Yearly trend over 20+ years of lake temperature in Rhode Island lakes and ponds.", display = "cite")`).
